A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-07 ECCV/paper.tex
Super Final version (Most probably)

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches from the image. In our case, it is used to detect portions
of the circular fiducials that were not affected by the blur. 
We applied the Gabor filter in eight
different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then $\ell^2$-norm of outputs along all orientations is calculated and finally
$\ell^2$-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
%% MBS - is the Kruizinga filter resonable to cite?

\noindent\textbf{Clustering}: The binarized Gabor filter responses are
treated as a set of connected components in the image.   Clustering
is used to find components that are located in a close spatial region.  We do
this via hierarchical clustering~\cite{ALGLIB} using unweighted
average linkage with a distance threshold set to 150.

\noindent\textbf{PCA}: For each clustered set of components, we apply
PCA to determine the dominant direction.  This is done by examining the
orientation of the first principal component.  We then extract an intensity
profile patch in the input image along this direction as it extends through the
bounding box of the cluster. The signature of this profile will be used to
identify the code.

@@

\noindent\textbf{Classification}: As mentioned above, a small image patch containing
the intensity profile of the fiducial is used to identify the code.   We found
that a training-based method using K-NN gave better results than trying to
find binary code directly by determining the presence (or absence) of ring
at particular positions in the image patch. To build the training-data, a
synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
, 350) with blur scale set to 40, and its intensity profile along the first
principal component from every output is taken as training data for that
fiducial pattern. Figure \ref{fig:training_data} shows the process of creating
training data for fiducial with binary code ``01'' embedded in it.  For an
input image patch, we normalize its intensity range and then compare it against
the training-data. The class label from the closest top $K=5$ images in the
training-data is used to label the patch.

>>>>

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches from the image. In our case, it is used to detect portions
of the circular fiducials that were not affected by the blur. 
We applied the Gabor filter in eight
different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then $\ell^2$-norm of outputs along all orientations is calculated and finally
$\ell^2$-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
%% MBS - is the Kruizinga filter resonable to cite?

\noindent\textbf{Clustering}~~The binarized Gabor filter responses are
treated as a set of connected components in the image.   Clustering
is used to find components that are located in a close spatial region.  We do
this via hierarchical clustering~\cite{ALGLIB} using unweighted
average linkage with a distance threshold set to 150.

\noindent\textbf{PCA}~~For each clustered set of components, we apply
PCA to determine the dominant direction.  This is done by examining the
orientation of the first principal component.  We then extract an intensity
profile patch in the input image along this direction as it extends through the
bounding box of the cluster. The signature of this profile will be used to
identify the code.

@@

\noindent\textbf{Classification}~~As mentioned above, a small image patch
containing the intensity profile of the fiducial is used to identify the code.   We found
that a training-based method using K-NN gave better results than trying to
find binary code directly by determining the presence (or absence) of ring
at particular positions in the image patch. To build the training-data, a
synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
, 350) with blur scale set to 40, and its intensity profile along the first
principal component from every output is taken as training data for that
fiducial pattern. Figure \ref{fig:training_data} shows the process of creating
training data for fiducial with binary code ``01'' embedded in it.  For an
input image patch, we normalize its intensity range and then compare it against
the training-data. The class label from the closest top $K=5$ images in the
training-data is used to label the patch.
